Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
Update manuscript.Rmd, manuscript.docx, and ~$nuscript.docx

---
title: Interisland movements of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
   ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
   ^2^Department of Biology, Memorial University of Newfoundland, Canada
   #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
  #  github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   bookdown::word_document2:
    #reference_docx: template.docx
bibliography: ../references/knitcite.bib
#csl: csl.csl
---

@@

Caribou may swim between islands in the ocean for similar reasons that drive
caribou swimming in freshwater [@Leblond_2016]. We present two
explanations for these swimming events, forage limitation (Miller 2002) and
predator avoidance [@Jeffrey_2007], and discuss why these swimming events
appear to be relatively commonplace in the population.

>>>>

---
title: Interisland movements and oceanic swimming of woodland caribou in Newfoundland
author: Quinn M.R. Webber^1\*^, Jack G. Hendrix^1^, Alec L. Robitaille^2^,  Eric Vander Wal^1,2^
date: 
   ^1^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
   ^2^Department of Biology, Memorial University of Newfoundland, Canada
   #\*Corresponding author: Quinn M.R. Webber (webber.quinn@gmail.com)
output: 
  #  github_document
  # bookdown::pdf_document2:
  #    number_sections: true
  #    toc: false
   bookdown::word_document2:
    #reference_docx: template.docx
bibliography: ../references/knitcite.bib
#csl: csl.csl
---

@@

Caribou may swim between islands in the ocean for similar reasons that drive
caribou swimming in freshwater [@Leblond_2016]. We present two
explanations for these swimming events, forage limitation (Miller 2002) and
predator avoidance [@Jeffery_2007], and discuss why these swimming events
appear to be relatively commonplace in the population.
